---
title: "Module 5 Report"
author: "ouRduino"
date: "2023-10-10"
output: html_document
bibliogrophy:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction
In this study, 

## Methods


## Results


```{r metadata, echo=FALSE, message=FALSE}
library(tidyverse)
dat.f <- list.files(pattern = "couch|active.csv") 

dat.l <- list() 

for(i in dat.f){
  met.dat <- unlist(strsplit(i,"_")) 
  who <- met.dat[1] 
  activity <- gsub(".csv","",met.dat[2]) 
  dat.l[[i]]<- read_csv(i) %>%
    mutate(who=who,activity=activity)
  
}

dat <- do.call(rbind,dat.l) 


dat%>%
  ggplot()+geom_boxplot(aes(x=activity,y=degC))+facet_grid(.~who) 
```

Our data did not show a significant correlation between activity and a higher body temperature. In the case of Alexandra, the median of the couch temperature readings were higher than that of the active temperature (~0.3 degrees C difference). It was the opposite in the Michael's data, as the median active temperature was ~0.25 degrees C higher than the inactive temperature median. 
(t test or anovag group factor temp explaines by activity + who)
## Discussion


## Author Contributions


## References


